---
title: CV
name: Daniel J.
surname: Hicks
position: "Assistant Professor of Philosophy"
address: "University of California, Merced"
www: dhicks.github.io
email: "dhicks4@ucmerced.edu"
github: dhicks
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "aboutmetext"
output: 
  vitae::markdowncv:
      theme: "davewhipp"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(fontawesome)
```

## Areas of interest

**Philosophy**: 
philosophy of science, ethics, social and political philosophy

**Science and Technology Studies**: 
science policy, environmental policy

**Data Science**: 
text mining, bibliometrics, philosophy of statistical modeling


## Professional appointments

```{r}
tribble(
    ~ title, ~ year, ~ department, ~ institution, 
    'Assistant Professor of Philosophy', '2019-', 'Department of Cognitive & Information Sciences', 'University of California, Merced', 
    'Postdoctoral Researcher', '2017-2019', 'Data Science Intiative', 'University of California, Davis', 
    'Science and Technology Policy Fellow', '2015-2017', '2015-16: Hosted by the Environmental Protection
Agency, Chemical Safety for Sustainability Program; 2016-17: Hosted by the National Science Foundation,
National Robotics Initiative', 'American Assocation for the Advancement of Science',
    'Postdoctoral Fellow', '2013-2015', 'Rotman Institute of Philosophy', 'University of Western Ontario', 
    'Postdoctoral Fellow', '2012-2013', 'College of Arts and Letters and Department of Philosophy', 'University of Notre Dame'
) |> 
    detailed_entries(institution, year, department, title)
```

## Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  'PhD, Philosophy', 2012, 'University of Notre Dame', 'Notre Dame, IN',
  'MS, Mathematics', 2003, 'University of Illinois, Chicago', 'Chicago, IL',
  'BS, Mathematics + Politics and Government', 2002, 'University of Puget Sound', 'Tacoma, WA'
  ) %>% 
  detailed_entries(Institution, Year, Where, Degree)
```


## Peer-reviewed publications

```{r}
## From <https://stackoverflow.com/questions/22870198/is-there-a-more-efficient-way-to-replace-null-with-na-in-a-list/49539022#49539022>
replace_x <- function(x, replacement = NA_character_) {
    if (length(x) == 0 || length(x[[1]]) == 0) {
        replacement
    } else {
        x
    }
}

bibliography_entries("peer_reviewed.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued))
```

## Other scholarly products

```{r}
bibliography_entries("other_scholarly.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued))
```

## Public talks and publications

```{r}
bibliography_entries("public.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued))
```

