---
title: "CV"
name: "Dan"
surname: "Hicks"
pronouns: "they/them"
position: "Associate Professor of Philosophy"
address: "University of California, Merced"
www: "dhicks.github.io"
orcid: "0000-0001-7945-4416"
email: "dhicks4@ucmerced.edu"
date: "`r format(Sys.time(), '%B %Y')`"
css: "theme.css"
# bibliography: "peer_reviewed.bib"
output: 
  vitae::markdowncv:
      theme: "kjhealy"
      keep_md: true
  vitae::moderncv:
      latex_engine: "xelatex"
      keep_tex: true
---

```{r filters, include=FALSE}
## NB If filters result in empty sections, need to suppress these here or LaTeX will throw an error
pub_filter = rlang::quo()
talk_filter = rlang::quo()
# pub_filter = rlang::quo(as.Date(issued) >= '2022-07-01')
# talk_filter = rlang::quo(when >= '2022-07-01')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
is_pdf = knitr::is_latex_output()
library(tidyverse)
library(vitae)
library(fontawesome)
library(googlesheets4)
library(gt)

format_dates = function(x) {
    mutate(x, when = stamp('October 1981', orders = 'BY')(when))
}

gs4_auth(email = "hicks.daniel.j@gmail.com")
```

## Areas of interest

**Philosophy**: 
philosophy of science, ethics, social and political philosophy

**Science and Technology Studies**: 
science policy, environmental policy

**Data Science**: 
text mining, bibliometrics, philosophy of statistical modeling


## Professional appointments

```{r}
tribble(
    ~ title, ~ year, ~ department, ~ institution, 
    'Department Chair', '2024-', 'Department of Philosophy', 'University of California, Merced',
    'Associate Professor of Philosophy', '2023-', 'Department of Philosophy; Affiliate Faculty, Public Health Graduate Group; Affiliate Faculty, Health Sciences Research Institute', 'University of California, Merced', 
    'Assistant Professor of Philosophy', '2019-2023', 'Department of Cognitive Science', 'University of California, Merced',
    'Postdoctoral Researcher', '2017-2019', 'Data Science Intiative', 'University of California, Davis', 
    'Science and Technology Policy Fellow', '2015-2017', '2015-16: Hosted by the Environmental Protection
Agency, Chemical Safety for Sustainability Program; 2016-17: Hosted by the National Science Foundation,
National Robotics Initiative', 'American Assocation for the Advancement of Science',
    'Postdoctoral Fellow', '2013-2015', 'Rotman Institute of Philosophy', 'University of Western Ontario', 
    'Postdoctoral Fellow', '2012-2013', 'College of Arts and Letters and Department of Philosophy', 'University of Notre Dame'
) |> 
    detailed_entries(institution, year, department, title)
```

## Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  'PhD, Philosophy', 2012, 'University of Notre Dame', 'Notre Dame, IN',
  'MS, Mathematics', 2003, 'University of Illinois, Chicago', 'Chicago, IL',
  'BS, Mathematics + Politics and Government', 2002, 'University of Puget Sound', 'Tacoma, WA'
  ) %>% 
  detailed_entries(Institution, Year, Where, Degree)
```



## Peer-reviewed publications

```{r}
## From <https://stackoverflow.com/questions/22870198/is-there-a-more-efficient-way-to-replace-null-with-na-in-a-list/49539022#49539022>
replace_x <- function(x, replacement = NA_character_) {
    if (length(x) == 0 || length(x[[1]]) == 0) {
        replacement
    } else {
        x
    }
}

bibliography_entries("peer_reviewed.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued)) |> 
    filter(!!pub_filter)
```


## Other scholarly products

```{r}
bibliography_entries("other_scholarly.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued)) |> 
    filter(!!pub_filter)
```


## General interest publications

```{r}
bibliography_entries("public.bib") |> 
    mutate(issued = modify_depth(issued, 1, replace_x)) |> 
    arrange(desc(issued)) |> 
    filter(!!pub_filter)
```

## Scholarly talks

```{r}
read_sheet('https://docs.google.com/spreadsheets/d/1nKDb1e4rmZBlp_KfDAJkQKRij4btkDewAH-hB6MnxT0/edit#gid=0', 
                 col_types = 'cDccc') |> 
    detailed_entries(what = what, when = when, with = where, where = with, why = why, .protect = is_pdf) |> 
    filter(!!talk_filter) |> 
    format_dates()
```

## Public and cross-disciplinary talks

```{r}
read_sheet('https://docs.google.com/spreadsheets/d/1Ply5ydXH25Vve1U9TZ_VZLsYL2f6dJIlv2L1Uaiw4Ew/edit#gid=0', 
           col_types = 'cDccc') |> 
    detailed_entries(what = what, when = when, with = where, where = with, why = why, 
                     .protect = is_pdf) |> 
    filter(!!talk_filter) |> 
    format_dates()
```


## Students and mentees

- Emilio Lobato (UC Merced, Ph.D., co-advisor)
- Daisy Underhill (UC Davis, Ph.D., prospectus committee member)
- Aaron Chavez (UC Davis, Ph.D., prospectus committee member)
- Dennis Perez (UC Merced, M.A., committee member)
- Anthony Sainez (UC Merced, undergraduate, research supervisor)
- Kaeda Sabrewing (UC Merced, undergraduate, research supervisor)
- Rebecca Korf (UC Irvine, Ph.D., committee member)
- Cosmo Campbell (UC Merced, undergraduate, research supervisor)
- Joseph Dad (UC Merced, undergraduate, research supervisor)

I have also mentored graduate students through the Underrepresented Philosophy of Science Scholars (UPSS) initiative of the PSA. 

- Kino Zhao (UC Irvine, Ph.D.)
- Michelle Pham (Univ. of Washington, 2020)

## Service

```{r, include=FALSE}
read_sheet('https://docs.google.com/spreadsheets/d/1nKDb1e4rmZBlp_KfDAJkQKRij4btkDewAH-hB6MnxT0/edit?gid=670362183#gid=670362183', 
           sheet = 'peer review') |> 
    # replace_na(list(venue = '', count = '')) |> 
    gt(caption = 'Peer review') |> 
    sub_missing(missing_text = '') |> 
    tab_options(column_labels.hidden = TRUE)
```

```{r}
read_sheet('https://docs.google.com/spreadsheets/d/1nKDb1e4rmZBlp_KfDAJkQKRij4btkDewAH-hB6MnxT0/edit?gid=670362183#gid=670362183', 
           sheet = 'service') |> 
    detailed_entries(what, when, with, why)
```
